---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fastdivrate

<!-- badges: start -->
[![R-CMD-check](https://github.com/jonchang/fastdivrate/workflows/R-CMD-check/badge.svg)](https://github.com/jonchang/fastdivrate/actions)
<!-- badges: end -->

The goal of fastdivrate is to quickly compute tip-specific diversification rates using a variety of statistics.

## Installation

Install the development version with:

``` r
if (!requireNamespace("remotes", quietly = TRUE))
    install.packages("remotes")

remotes::install_github("jonchang/fastdivrate")
```

Once this is accepted on CRAN, you could install the released version of fastdivrate from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fastdivrate")
```

(Note: Not on CRAN just yet.)

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(fastdivrate)
library(ape)
# Simulate a big tree
tree <- rcoal(10000)
# Calculate its diversification rates, quickly
rates <- DR_statistic_C(tree)
stem(rates)
```
